### 2018-05-07 doc/paper.tex
Updating plots with a priori bounds.
Also

- adding example coefficient functions for bounds
  when K = 1, 2, 3, 4
- adding a sketch of a proof for Lemma 4.2.

@@

  \begin{algorithmic}
    \Function{\(\widehat{\ell} =
        \mathtt{LocalError}\)}{$e, \rho, \delta b$}
      \State \(L = \texttt{length}(e)\)
      \\
      \State \(\widehat{\ell} = e_1 \oplus e_2\)
      \For{\(j = 3, \ldots, L\)}
        \State \(\widehat{\ell} = \widehat{\ell} \oplus e_j\)
      \EndFor
      \\
      \State \(\widehat{\ell} = \widehat{\ell} \oplus \left(\rho \otimes \delta b\right)\)
    \EndFunction
  \end{algorithmic}
\end{breakablealgorithm}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:ell-tilde}]
Coming soon.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lemma:L-and-D-bounds}]
First, note that for \textbf{any} sequence \(v_0, \ldots, v_{k + 1}\) we
must have
\begin{equation}
\sum_{j = 0}^k \left[(1 - s) v_j + s v_{j + 1}\right] B_{j, k}(s) =
\sum_{j = 0}^{k + 1} v_j B_{j, k + 1}(s).
\end{equation}
For example of this in use, via \eqref{ell-tilde-1}, we have
\begin{equation}
  L_{1, k} \leq \gamma_3 \sum_{j = 0}^{k + 1} \left|
  \widehat{b}_j^{(k + 1)}\right| B_{j, k + 1}(s).
\end{equation}
In order to work with sums of this form, we define Bernstein-type
sums related to \(L_{F, k}\):
\begin{align}
D_{0, k} &\coloneqq \sum_{j = 0}^k \left|\widehat{b}_j^{(k)}\right|
B_{j, k}(s) \\
D_{F, k} &\coloneqq \sum_{j = 0}^k \left|\cdb{F}_j^{(k)}\right| B_{j, k}(s).
\end{align}
Hence Lemma~\ref{lemma:ell-tilde} gives
\begin{align}
L_{1, k} &\leq \gamma_3 D_{0, k + 1} \label{ell-1-k} \\
L_{F + 1, k} &\leq \gamma_3 D_{F, k + 1} + \gamma_{5F} L_{F, k}
\label{ell-F-k}
\end{align}
In addition, for \(F \geq 1\) since
\begin{align}
\cdb{F}_j^{(k)} &= \widehat{\ell}_{F, j}^{(k)} \oplus \left(
  s \otimes \cdb{F}_{j + 1}^{(k + 1)}\right) \oplus \left((1 \ominus s) \otimes
  \cdb{F}_{j}^{(k + 1)}\right) \\
&= (1 - s) \cdot \cdb{F}_j^{(k + 1)}(1 + \theta_3) +
  s \cdot \cdb{F}_{j + 1}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F, j}^{(k)} (1 + \theta_2)
\end{align}
we have
\begin{equation}\label{df-first}
D_{F, k} \leq (1 + \gamma_3) D_{F, k + 1} + (1 + \gamma_2) \sum_{j = 0}^k
\left|\widehat{\ell}_{F, j}^{(k)}\right| B_{j, k}(s).
\end{equation}
Since \(\ell_{F, j}^{(k)}\) has \(5F - 1\) terms (only the last of which
involves a product), the terms in the computed value will be involved in
at most \(5F - 2\) flops, hence
\(\left|\widehat{\ell}_{F, j}^{(k)}\right| \leq
\left(1 + \gamma_{5F - 2}\right) \widetilde{\ell}_{F, j}^{(k)}.\)
Combined with \eqref{df-first} and the fact that there is no local error
when \(F = 0\), this means
\begin{align}
D_{0, k} &\leq (1 + \gamma_3) D_{0, k + 1} \label{d-0-k} \\
D_{F, k} &\leq (1 + \gamma_3) D_{F, k + 1} + (1 + \gamma_{5F}) L_{F, k}.
\label{d-F-k}
\end{align}
The four inequalities \eqref{ell-1-k}, \eqref{ell-F-k}, \eqref{d-0-k}
and \eqref{d-F-k} allow us to write all bounds in terms of
\(D_{0, n} = \widetilde{p}(s)\) and \(D_{F, n} = 0\). From \eqref{d-0-k}
we can conclude that \(D_{0, n - k} \leq \left(1 + \gamma_{3k}\right) \cdot
\widetilde{p}(s)\) and from \eqref{ell-1-k} that \(L_{1, n - k} \leq
\gamma_3 \left(1 + \gamma_{3(k - 1)}\right) \cdot \widetilde{p}(s)\).

>>>>

For the first few values of \(K\) the coefficient of
\(\cond{p, s}\) in the bound is
\begin{center}
  \begin{tabular}{>{$}c<{$} c >{$}c<{$}}
    K & Method & \text{Multiplier} \\
    \midrule
    1 & \texttt{DeCasteljau} & 3 \binom{n}{1} \mach =
      3n \mach \approx \gamma_{3n} \\[0.125cm]
    2 & \texttt{CompDeCasteljau} & \left[9 \binom{n}{2} +
      15 \binom{n}{1}\right]\mach^2 = \frac{3n(3n + 7)}{2} \mach^2
      \approx \frac{1}{4} \cdot 2 \gamma_{3n}^2 \\[0.125cm]
    3 & \texttt{CompDeCasteljau3} & \left[27 \binom{n}{3} +
      135 \binom{n}{2} + 150 \binom{n}{1}\right] \mach^3 =
      \frac{3n(3n^2 + 36n + 61)}{2} \mach^3 \\[0.125cm]
    4 & \texttt{CompDeCasteljau4} & \left[81 \binom{n}{4} + 810 \binom{n}{3} +
      2475 \binom{n}{2} + 2250 \binom{n}{1}\right] \mach^4 \\[0.125cm]
  \end{tabular}
\end{center}
See the \hyperref[proof:L-and-D-bounds]{proof} of
Lemma~\ref{lemma:L-and-D-bounds} for more details on where these
polynomials come from.

@@

  \begin{algorithmic}
    \Function{\(\widehat{\ell} =
        \mathtt{LocalError}\)}{$e, \rho, \delta b$}
      \State \(L = \texttt{length}(e)\)
      \\
      \State \(\widehat{\ell} = e_1 \oplus e_2\)
      \For{\(j = 3, \ldots, L\)}
        \State \(\widehat{\ell} = \widehat{\ell} \oplus e_j\)
      \EndFor
      \\
      \State \(\widehat{\ell} = \widehat{\ell} \oplus \left(
          \rho \otimes \delta b\right)\)
    \EndFunction
  \end{algorithmic}
\end{breakablealgorithm}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:ell-tilde}]
We'll start with the \(F = 1\) case. Recall where the terms originate:
\begin{align}
\left[P_1, e_1\right] &= \mathtt{TwoProd}\left(\widehat{r},
  \widehat{b}_j^{(k + 1)}\right) \\
\left[P_2, e_2\right] &= \mathtt{TwoProd}\left(s,
  \widehat{b}_{j + 1}^{(k + 1)}\right) \\
\left[\widehat{b}_j^{(k)}, e_3\right] &= \mathtt{TwoSum}\left(P_1, P_2\right).
\end{align}
Hence Theorem~\ref{thm:eft} tells us that
\begin{align}
\left|P_1\right| &\leq (1 + \mach)\left|\widehat{r} \cdot
  \widehat{b}_j^{(k + 1)}\right| \leq (1 + \mach)^2 (1 - s)
  \left|\widehat{b}_j^{(k + 1)}\right| \\
\left|e_1\right| &\leq \mach \left|\widehat{r} \cdot
  \widehat{b}_j^{(k + 1)}\right| \leq \mach(1 + \mach)(1 - s) \left|
  \widehat{b}_j^{(k + 1)}\right| \\
\left|P_2\right| &\leq (1 + \mach) s \left|\widehat{b}_{j + 1}^{(k + 1)}\right| \\
\left|e_2\right| &\leq \mach s \left|\widehat{b}_{j + 1}^{(k + 1)}\right| \\
\left|e_3\right| &\leq \mach \left|P_1\right| + \mach\left|P_2\right| \\
\left|\rho \cdot \widehat{b}_j^{(k + 1)}\right| &\leq
(1 + \mach)(1 - s) \left|\widehat{b}_j^{(k + 1)}\right|.
\end{align}
In general, we can swap \(\mach\left|P_j\right|\) for
\((1 + \mach)\left|e_j\right|\) based on how closely related the bound
on the result and the bound on the error are. Thus
\begin{align}
\widetilde{\ell}_{1, j}^{(k)} &= \left|e_1\right| + \left|e_2\right| +
  \left|e_3\right| + \left|\rho \cdot \widehat{b}_j^{(k + 1)}\right| \\
&\leq (2 + \mach)\left(\left|e_1\right| + \left|e_2\right|\right) +
  (1 + \mach)(1 - s) \left|\widehat{b}_j^{(k + 1)}\right| \\
&\leq \left[(1 + \mach)^3 - 1\right] (1 - s) \left|
  \widehat{b}_j^{(k + 1)}\right| + \left[(1 + \mach)^2 - 1\right] s \left|
  \widehat{b}_{j + 1}^{(k + 1)}\right| \\
&\leq \gamma_3 \left((1 - s) \left|\widehat{b}_j^{(k + 1)}\right| +
  s \left|\widehat{b}_{j + 1}^{(k + 1)}\right|\right).
\end{align}
For \(\widetilde{\ell}_{F + 1}\), we want to relate the ``current'' errors
\(e_1, \ldots, e_{5F + 3}\) to the ``previous'' errors \(e_1',
\ldots, e_{5F - 2}'\). In the same fashion as above, we track where
the current errors come from:
\begin{align}
\left[S_1, e_1\right] &= \mathtt{TwoSum}\left(e_1', e_2'\right) \\
\left[S_2, e_2\right] &= \mathtt{TwoSum}\left(S_1, e_3'\right) \\
&\mathrel{\makebox[\widthof{=}]{\vdots}} \nonumber \\
\left[S_{5F - 3}, e_{5F - 3}\right] &=
  \mathtt{TwoSum}\left(S_{5F - 4}, e_{5F - 2}'\right) \\
\left[P_{5F - 2}, e_{5F - 2}\right] &= \mathtt{TwoProd}\left(\rho,
  \cdb{F - 1}_j^{(k + 1)}\right) \\
\left[\widehat{\ell}_{F, j}^{(k)}, e_{5F - 1}\right] &=
  \mathtt{TwoSum}\left(S_{5F - 3}, P_{5F - 2}\right) \\
\left[P_{5F}, e_{5F}\right] &= \mathtt{TwoProd}\left(s,
  \cdb{F}_{j + 1}^{(k + 1)}\right) \\
\left[S_{5F + 1}, e_{5F + 1}\right] &=
  \mathtt{TwoSum}\left(\widehat{\ell}_{F, j}^{(k)}, P_{5F}\right) \\
\left[P_{5F + 2}, e_{5F + 2}\right] &= \mathtt{TwoProd}\left(\rho,
  \cdb{F}_j^{(k + 1)}\right) \\
\left[\cdb{F}_j^{(k)}, e_{5F + 3}\right] &= \mathtt{TwoSum}\left(
  S_{5F + 1}, P_{5F + 2}\right).
\end{align}
Arguing as we did above, we start with
\(\left|e_1\right| \leq \mach \left|e_1'\right| + \mach \left|e_2'\right|\)
and build each bound recursively based on the previous, e.g.
\(\left|e_2\right| \leq \mach \left|S_1\right| + \mach \left|e_3'\right| \leq
(1 + \mach) \mach \left|e_1'\right| + (1 + \mach) \mach \left|e_2'\right| +
\mach \left|e_3'\right|\). Proceeding in this fashion, we find
\begin{align}
\widetilde{\ell}_{F + 1, j}^{(k)} &= \left|e_1\right| + \cdots +
  \left|e_{5F + 3}\right| + \left|\rho \cdot \cdb{F}_j^{(k + 1)}\right| \\
&\leq \gamma_{5F} \left|e_1'\right| + \gamma_{5F} \left|e_2'\right| +
  \gamma_{5F - 1} \left|e_3'\right| + \cdots +
  \gamma_4 \left|e_{5F - 2}'\right| +
  \gamma_4 \left|\rho \cdot \cdb{F - 1}_j^{(k + 1)}\right| \\
&\qquad + \gamma_3 (1 - s) \left|
  \cdb{F}_j^{(k + 1)}\right| + \gamma_3 s \left|
  \cdb{F}_{j + 1}^{(k + 1)}\right| \\
&\leq \gamma_3 \left(
  (1 - s) \left|\cdb{F}_j^{(k + 1)}\right| +
  s \left|\cdb{F}_{j + 1}^{(k + 1)}\right|\right) +
  \gamma_{5F} \cdot \widetilde{\ell}_{F, j}^{(k)}
\end{align}
as desired.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lemma:L-and-D-bounds}]\label{proof:L-and-D-bounds}
First, note that for \textbf{any} sequence \(v_0, \ldots, v_{k + 1}\) we
must have
\begin{equation}
\sum_{j = 0}^k \left[(1 - s) v_j + s v_{j + 1}\right] B_{j, k}(s) =
\sum_{j = 0}^{k + 1} v_j B_{j, k + 1}(s).
\end{equation}
For example of this in use, via \eqref{ell-tilde-1}, we have
\begin{equation}
  L_{1, k} \leq \gamma_3 \sum_{j = 0}^{k + 1} \left|
  \widehat{b}_j^{(k + 1)}\right| B_{j, k + 1}(s).
\end{equation}
In order to work with sums of this form, we define Bernstein-type
sums related to \(L_{F, k}\):
\begin{align}
D_{0, k} &\coloneqq \sum_{j = 0}^k \left|\widehat{b}_j^{(k)}\right|
B_{j, k}(s) \\
D_{F, k} &\coloneqq \sum_{j = 0}^k \left|\cdb{F}_j^{(k)}\right| B_{j, k}(s).
\end{align}
Hence Lemma~\ref{lemma:ell-tilde} gives
\begin{align}
L_{1, k} &\leq \gamma_3 D_{0, k + 1} \label{ell-1-k} \\
L_{F + 1, k} &\leq \gamma_3 D_{F, k + 1} + \gamma_{5F} L_{F, k}
\label{ell-F-k}
\end{align}
In addition, for \(F \geq 1\) since
\begin{align}
\cdb{F}_j^{(k)} &= \widehat{\ell}_{F, j}^{(k)} \oplus \left(
  s \otimes \cdb{F}_{j + 1}^{(k + 1)}\right) \oplus \left((1 \ominus s) \otimes
  \cdb{F}_{j}^{(k + 1)}\right) \\
&= (1 - s) \cdot \cdb{F}_j^{(k + 1)}(1 + \theta_3) +
  s \cdot \cdb{F}_{j + 1}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F, j}^{(k)} (1 + \theta_2)
\end{align}
we have
\begin{equation}\label{df-first}
D_{F, k} \leq (1 + \gamma_3) D_{F, k + 1} + (1 + \gamma_2) \sum_{j = 0}^k
\left|\widehat{\ell}_{F, j}^{(k)}\right| B_{j, k}(s).
\end{equation}
Since \(\ell_{F, j}^{(k)}\) has \(5F - 1\) terms (only the last of which
involves a product), the terms in the computed value will be involved in
at most \(5F - 2\) flops, hence
\(\left|\widehat{\ell}_{F, j}^{(k)}\right| \leq
\left(1 + \gamma_{5F - 2}\right) \widetilde{\ell}_{F, j}^{(k)}.\)
Combined with \eqref{df-first} and the fact that there is no local error
when \(F = 0\), this means
\begin{align}
D_{0, k} &\leq (1 + \gamma_3) D_{0, k + 1} \label{d-0-k} \\
D_{F, k} &\leq (1 + \gamma_3) D_{F, k + 1} + (1 + \gamma_{5F}) L_{F, k}.
\label{d-F-k}
\end{align}
The four inequalities \eqref{ell-1-k}, \eqref{ell-F-k}, \eqref{d-0-k}
and \eqref{d-F-k} allow us to write all bounds in terms of
\(D_{0, n} = \widetilde{p}(s)\) and \(D_{F, n} = 0\). From \eqref{d-0-k}
we can conclude that \(D_{0, n - k} \leq \left(1 + \gamma_{3k}\right) \cdot
\widetilde{p}(s)\) and from \eqref{ell-1-k} that \(L_{1, n - k} \leq
\gamma_3 \left(1 + \gamma_{3(k - 1)}\right) \cdot \widetilde{p}(s)\).
